---
  title: "BIOS 611 HW11 Iteration (Chapter 21)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

# Exercise 1

1.  Write for loops to:

    Answer: 

    ```{r}

    ```

    1. Compute the mean of every column in `mtcars`.
    Answer: 

    ```{r}

    ```

    1. Determine the type of each column in `nycflights13::flights`.
    Answer: 

    ```{r}

    ```

    1. Compute the number of unique values in each column of `iris`.
    Answer: 

    ```{r}

    ```

    1. Generate 10 random normals for each of $\mu = -10$, $0$, $10$, and $100$.
    
    Think about the output, sequence, and body __before__ you start writing
    the loop.

    Answer: 

    ```{r}

    ```

2.  Eliminate the for loop in each of the following examples by taking 
    advantage of an existing function that works with vectors:
    
    ```{r, eval = FALSE}
    out <- ""
    for (x in letters) {
      out <- stringr::str_c(out, x)
    }
    
    x <- sample(100)
    sd <- 0
    for (i in seq_along(x)) {
      sd <- sd + (x[i] - mean(x)) ^ 2
    }
    sd <- sqrt(sd / (length(x) - 1))
    
    x <- runif(100)
    out <- vector("numeric", length(x))
    out[1] <- x[1]
    for (i in 2:length(x)) {
      out[i] <- out[i - 1] + x[i]
    }
    ```

    Answer: 

    ```{r}

    ```

3.  Combine your function writing and for loop skills:

    Answer: 

    ```{r}

    ```

    1. Write a for loop that `prints()` the lyrics to the children's song 
       "Alice the camel".

    Answer: 

    ```{r}

    ```

    1. Convert the nursery rhyme "ten in the bed" to a function. Generalise 
       it to any number of people in any sleeping structure.

    Answer: 

    ```{r}

    ```

    1. Convert the song "99 bottles of beer on the wall" to a function.
       Generalise to any number of any vessel containing any liquid on 
       any surface.

    Answer: 

    ```{r}

    ```

4.  It's common to see for loops that don't preallocate the output and instead
    increase the length of a vector at each step:
    
    ```{r, eval = FALSE}
    output <- vector("integer", 0)
    for (i in seq_along(x)) {
      output <- c(output, lengths(x[[i]]))
    }
    output
    ```
    
    How does this affect performance? Design and execute an experiment.

    Answer: 

    ```{r}

    ```

# Exercise 2

1.  Imagine you have a directory full of CSV files that you want to read in.
    You have their paths in a vector, 
    `files <- dir("data/", pattern = "\\.csv$", full.names = TRUE)`, and now
    want to read each one with `read_csv()`. Write the for loop that will 
    load them into a single data frame. 

    Answer: 

    ```{r}

    ```

2.  What happens if you use `for (nm in names(x))` and `x` has no names?
    What if only some of the elements are named? What if the names are
    not unique?

    Answer: 

    ```{r}

    ```

3.  Write a function that prints the mean of each numeric column in a data 
    frame, along with its name. For example, `show_mean(iris)` would print:
    
    ```{r, eval = FALSE}
    show_mean(iris)
    #> Sepal.Length: 5.84
    #> Sepal.Width:  3.06
    #> Petal.Length: 3.76
    #> Petal.Width:  1.20
    ```
    
    (Extra challenge: what function did I use to make sure that the numbers
    lined up nicely, even though the variable names had different lengths?)

    Answer: 

    ```{r}

    ```

4.  What does this code do? How does it work?

    ```{r, eval = FALSE}
    trans <- list( 
      disp = function(x) x * 0.0163871,
      am = function(x) {
        factor(x, labels = c("auto", "manual"))
      }
    )
    for (var in names(trans)) {
      mtcars[[var]] <- trans[[var]](mtcars[[var]])
    }
    ```

    Answer: 

    ```{r}

    ```

# Exercise 3

1.  Read the documentation for `apply()`. In the 2d case, what two for loops
    does it generalise?

    Answer: 

    ```{r}

    ```

2.  Adapt `col_summary()` so that it only applies to numeric columns
    You might want to start with an `is_numeric()` function that returns
    a logical vector that has a TRUE corresponding to each numeric column.

    Answer: 

    ```{r}

    ```

# Exercise 4

1.  Write code that uses one of the map functions to:

    Answer: 

    ```{r}

    ```

    1. Compute the mean of every column in `mtcars`.
    Answer: 

    ```{r}

    ```

    1. Determine the type of each column in `nycflights13::flights`.
    Answer: 

    ```{r}

    ```

    1. Compute the number of unique values in each column of `iris`.
    Answer: 

    ```{r}

    ```

    1. Generate 10 random normals for each of $\mu = -10$, $0$, $10$, and $100$.

    Answer: 

    ```{r}

    ```

2.  How can you create a single vector that for each column in a data frame
    indicates whether or not it's a factor?

    Answer: 

    ```{r}

    ```

3.  What happens when you use the map functions on vectors that aren't lists?
    What does `map(1:5, runif)` do? Why?
    
    Answer: 

    ```{r}

    ```

4.  What does `map(-2:2, rnorm, n = 5)` do? Why?
    What does `map_dbl(-2:2, rnorm, n = 5)` do? Why?

    Answer: 

    ```{r}

    ```

5.  Rewrite `map(x, function(df) lm(mpg ~ wt, data = df))` to eliminate the 
    anonymous function. 

    Answer: 

    ```{r}

    ```

# Exercise 5

1.  Implement your own version of `every()` using a for loop. Compare it with
    `purrr::every()`. What does purrr's version do that your version doesn't?

    Answer: 

    ```{r}

    ```

2.  Create an enhanced `col_sum()` that applies a summary function to every
    numeric column in a data frame.

    Answer: 

    ```{r}

    ```

3.  A possible base R equivalent of `col_sum()` is:

    ```{r}
    col_sum3 <- function(df, f) {
      is_num <- sapply(df, is.numeric)
      df_num <- df[, is_num]

      sapply(df_num, f)
    }
    ```
    
    But it has a number of bugs as illustrated with the following inputs:
    
    ```{r, eval = FALSE}
    df <- tibble(
      x = 1:3, 
      y = 3:1,
      z = c("a", "b", "c")
    )
    # OK
    col_sum3(df, mean)
    # Has problems: don't always return numeric vector
    col_sum3(df[1:2], mean)
    col_sum3(df[1], mean)
    col_sum3(df[0], mean)
    ```
    
    What causes the bugs?
    Answer: 

    ```{r}

    ```

