---
  title: "BIOS 611 HW8 Factors (Chapter 15)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

### Exercise

1.  Explore the distribution of `rincome` (reported income). What makes the
    default bar chart hard to understand? How could you improve the plot?

    Answer: 

    ```{r}

    ```

2.  What is the most common `relig` in this survey? What's the most
    common `partyid`?

    Answer: 

    ```{r}

    ```

3.  Which `relig` does `denom` (denomination) apply to? How can you find
    out with a table? How can you find out with a visualisation?

    Answer: 

    ```{r}

    ```

# Exercise 2

1.  There are some suspiciously high numbers in `tvhours`. Is the mean a good
    summary?

    Answer: 

    ```{r}

    ```

2.  For each factor in `gss_cat` identify whether the order of the levels is
    arbitrary or principled.

    Answer: 

    ```{r}

    ```

3.  Why did moving "Not applicable" to the front of the levels move it to the
    bottom of the plot?

    Answer: 

    ```{r}

    ```

# Exercise 3

1.  How have the proportions of people identifying as Democrat, Republican, and
    Independent changed over time?

    Answer: 

    ```{r}

    ```

2.  How could you collapse `rincome` into a small set of categories?
    Answer: 

    ```{r}

    ```

