---
  title: "BIOS 611 HW1 Data visualisation (Chapter 3)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

# Exercise 1

1.  Run `ggplot(data = mpg)`. What do you see?

    Answer: 

    ```{r}

    ```

2.  How many rows are in `mpg`? How many columns?

    Answer: 

    ```{r}

    ```

3.  What does the `drv` variable describe?  Read the help for `?mpg` to find
    out.
     
    Answer: 

    ```{r}

    ```

4.  Make a scatterplot of `hwy` vs `cyl`.

    Answer: 

    ```{r}

    ```

5.  What happens if you make a scatterplot of `class` vs `drv`? Why is
    the plot not useful?

    Answer: 

    ```{r}

    ```

# Exercise 2

1.  What's gone wrong with this code? Why are the points not blue?

    ```{r}
    ggplot(data = mpg) + 
      geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
    ```
    
    Answer: 

    ```{r}

    ```

2.  Which variables in `mpg` are categorical? Which variables are continuous? 
    (Hint: type `?mpg` to read the documentation for the dataset). How
    can you see this information when you run `mpg`?

    Answer: 

    ```{r}

    ```

3.  Map a continuous variable to `color`, `size`, and `shape`. How do
    these aesthetics behave differently for categorical vs. continuous
    variables? 
    
    Answer: 

    ```{r}

    ```

4.  What happens if you map the same variable to multiple aesthetics? 

    Answer: 

    ```{r}

    ```

5.  What does the `stroke` aesthetic do? What shapes does it work with?
    (Hint: use `?geom_point`)
    
    Answer: 

    ```{r}

    ```

6.  What happens if you map an aesthetic to something other than a variable 
    name, like `aes(colour = displ < 5)`?  

    Answer: 

    ```{r}

    ```

# Exercise 3

1.  What happens if you facet on a continuous variable?

    Answer: 

    ```{r}

    ```

2.  What do the empty cells in plot with `facet_grid(drv ~ cyl)` mean?
    How do they relate to this plot?
    
    ```{r, eval = FALSE}
    ggplot(data = mpg) + 
      geom_point(mapping = aes(x = drv, y = cyl))
    ```

    Answer: 

    ```{r}

    ```

3.  What plots does the following code make? What does `.` do?

    ```{r eval = FALSE}
    ggplot(data = mpg) + 
      geom_point(mapping = aes(x = displ, y = hwy)) +
      facet_grid(drv ~ .)
    
    ggplot(data = mpg) + 
      geom_point(mapping = aes(x = displ, y = hwy)) +
      facet_grid(. ~ cyl)
    ```

    Answer: 

    ```{r}

    ```

4.  Take the first faceted plot in this section:

    ```{r, eval = FALSE}
    ggplot(data = mpg) + 
      geom_point(mapping = aes(x = displ, y = hwy)) + 
      facet_wrap(~ class, nrow = 2)
    ```
    
    What are the advantages to using faceting instead of the colour aesthetic?
    What are the disadvantages? How might the balance change if you had a 
    larger dataset?
    
    Answer: 

    ```{r}

    ```

5.  Read `?facet_wrap`. What does `nrow` do? What does `ncol` do? What other
    options control the layout of the individual panels? Why doesn't
    `facet_grid()` have `nrow` and `ncol` arguments?

    Answer: 

    ```{r}

    ```

6.  When using `facet_grid()` you should usually put the variable with more
    unique levels in the columns. Why?

    Answer: 

    ```{r}

    ```

# Exercise 4

1.  What geom would you use to draw a line chart? A boxplot? 
    A histogram? An area chart?

    Answer: 

    ```{r}

    ```

2.  Run this code in your head and predict what the output will look like.
    Then, run the code in R and check your predictions.
    
    ```{r, eval = FALSE}
    ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
      geom_point() + 
      geom_smooth(se = FALSE)
    ```

    Answer: 

    ```{r}

    ```

3.  What does `show.legend = FALSE` do?  What happens if you remove it?  
    Why do you think I used it earlier in the chapter?

    Answer: 

    ```{r}

    ```

4.  What does the `se` argument to `geom_smooth()` do?


    Answer: 

    ```{r}

    ```

5.  Will these two graphs look different? Why/why not?

    ```{r, eval = FALSE}
    ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
      geom_point() + 
      geom_smooth()
    
    ggplot() + 
      geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
      geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
    ```

    Answer: 

    ```{r}

    ```

6.  Recreate the R code necessary to generate the following graphs.
    
    ```{r echo = FALSE, fig.width = 3, out.width = "50%", fig.align = "default", message = FALSE}
    ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
      geom_point() + 
      geom_smooth(se = FALSE)
    ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
      geom_smooth(aes(group = drv), se = FALSE) +
      geom_point()
    ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
      geom_point() + 
      geom_smooth(se = FALSE)
    ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
      geom_point(aes(color = drv)) + 
      geom_smooth(se = FALSE)
    ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
      geom_point(aes(color = drv)) +
      geom_smooth(aes(linetype = drv), se = FALSE)
    ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
      geom_point(size = 4, colour = "white") + 
      geom_point(aes(colour = drv))
    ```

    Answer: 

    ```{r}

    ```

# Exercise 5

1.  What is the default geom associated with `stat_summary()`? How could
    you rewrite the previous plot to use that geom function instead of the 
    stat function?

    Answer: 

    ```{r}

    ```

2.  What does `geom_col()` do? How is it different to `geom_bar()`?

    Answer: 

    ```{r}

    ```

3.  Most geoms and stats come in pairs that are almost always used in 
    concert. Read through the documentation and make a list of all the 
    pairs. What do they have in common?

    Answer: 

    ```{r}

    ```

4.  What variables does `stat_smooth()` compute? What parameters control
    its behaviour?

    Answer: 

    ```{r}

    ```

5.  In our proportion bar chart, we need to set `group = 1`. Why? In other
    words what is the problem with these two graphs?
    
    ```{r, eval = FALSE}
    ggplot(data = diamonds) + 
      geom_bar(mapping = aes(x = cut, y = ..prop..))
    ggplot(data = diamonds) + 
      geom_bar(mapping = aes(x = cut, fill = color, y = ..prop..))
    ```
  

    Answer: 

    ```{r}

    ```

# Exercise 6

1.  What is the problem with this plot? How could you improve it?

    ```{r}
    ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
      geom_point()
    ```

    Answer: 

    ```{r}

    ```

2.  What parameters to `geom_jitter()` control the amount of jittering?

    Answer: 

    ```{r}

    ```

3.  Compare and contrast `geom_jitter()` with `geom_count()`.

    Answer: 

    ```{r}

    ```

4.  What's the default position adjustment for `geom_boxplot()`? Create
    a visualisation of the `mpg` dataset that demonstrates it.

    Answer: 

    ```{r}

    ```

# Exercise 7

1.  Turn a stacked bar chart into a pie chart using `coord_polar()`.

    Answer: 

    ```{r}

    ```

2.  What does `labs()` do? Read the documentation.

    Answer: 

    ```{r}

    ```

3.  What's the difference between `coord_quickmap()` and `coord_map()`?

    Answer: 

    ```{r}

    ```

4.  What does the plot below tell you about the relationship between city
    and highway mpg? Why is `coord_fixed()` important? What does 
    `geom_abline()` do?
    
    ```{r, fig.asp = 1, out.width = "50%"}
    ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
      geom_point() + 
      geom_abline() +
      coord_fixed()
    ```

    Answer: 

    ```{r}

    ```

