---
  title: "BIOS 611 HW12 Graphics for communication (Chapter 28)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

# Exercise 1

1.  Create one plot on the fuel economy data with customised `title`,
    `subtitle`, `caption`, `x`, `y`, and `colour` labels.

    Answer: 

    ```{r}

    ```

2.  The `geom_smooth()` is somewhat misleading because the `hwy` for
    large engines is skewed upwards due to the inclusion of lightweight
    sports cars with big engines. Use your modelling tools to fit and display
    a better model.

    Answer: 

    ```{r}

    ```

3.  Take an exploratory graphic that you've created in the last month, and add
    informative titles to make it easier for others to understand.

    Answer: 

    ```{r}

    ```

# Exercise 2

1.  Use `geom_text()` with infinite positions to place text at the
    four corners of the plot.

    Answer: 

    ```{r}

    ```

2.  Read the documentation for `annotate()`. How can you use it to add a text
    label to a plot without having to create a tibble?

    Answer: 

    ```{r}

    ```

3.  How do labels with `geom_text()` interact with faceting? How can you
    add a label to a single facet? How can you put a different label in
    each facet? (Hint: think about the underlying data.)

    Answer: 

    ```{r}

    ```

4.  What arguments to `geom_label()` control the appearance of the background
    box?

    Answer: 

    ```{r}

    ```

5.  What are the four arguments to `arrow()`? How do they work? Create a series
    of plots that demonstrate the most important options.

    Answer: 

    ```{r}

    ```

# Exercise 3

1.  Why doesn't the following code override the default scale?

    ```{r fig.show = "hide"}
    ggplot(df, aes(x, y)) +
      geom_hex() +
      scale_colour_gradient(low = "white", high = "red") +
      coord_fixed()
    ```

    Answer: 

    ```{r}

    ```

2.  What is the first argument to every scale? How does it compare to `labs()`?

    Answer: 

    ```{r}

    ```

3.  Change the display of the presidential terms by:

    Answer: 

    ```{r}

    ```

    1. Combining the two variants shown above.
    Answer: 

    ```{r}

    ```

    1. Improving the display of the y axis.
    Answer: 

    ```{r}

    ```

    1. Labelling each term with the name of the president.
    Answer: 

    ```{r}

    ```

    1. Adding informative plot labels.
    Answer: 

    ```{r}

    ```

    1. Placing breaks every 4 years (this is trickier than it seems!).

    Answer: 

    ```{r}

    ```

4.  Use `override.aes` to make the legend on the following plot easier to see.

    ```{r, dev = "png", out.width = "50%"}
    ggplot(diamonds, aes(carat, price)) +
      geom_point(aes(colour = cut), alpha = 1/20)
    ```

    Answer: 

    ```{r}

    ```

