---
  title: "BIOS 611 HW10 Vectors (Chapter 20)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

# Exercise 1

1.  Describe the difference between `is.finite(x)` and  `!is.infinite(x)`.

    Answer: 

    ```{r}

    ```

2.  Read the source code for `dplyr::near()` (Hint: to see the source code,
    drop the `()`). How does it work? 

    Answer: 

    ```{r}

    ```

3.  A logical vector can take 3 possible values. How many possible
    values can an integer vector take? How many possible values can
    a double take? Use google to do some research.

    Answer: 

    ```{r}

    ```

4.  Brainstorm at least four functions that allow you to convert a double to an
    integer. How do they differ? Be precise.
    
    Answer: 

    ```{r}

    ```

5.  What functions from the readr package allow you to turn a string
    into logical, integer, and double vector?

    Answer: 

    ```{r}

    ```

# Exercise 2

1.  What does `mean(is.na(x))` tell you about a vector `x`? What about
    `sum(!is.finite(x))`?

    Answer: 

    ```{r}

    ```

2.  Carefully read the documentation of `is.vector()`. What does it actually
    test for? Why does `is.atomic()` not agree with the definition of 
    atomic vectors above?
    
    Answer: 

    ```{r}

    ```

3.  Compare and contrast `setNames()` with `purrr::set_names()`.

    Answer: 

    ```{r}

    ```

4.  Create functions that take a vector as input and returns:
    
    Answer: 

    ```{r}

    ```

    1. The last value.  Should you use `[` or `[[`?

    Answer: 

    ```{r}

    ```

    1. The elements at even numbered positions.
    
    Answer: 

    ```{r}

    ```

    1. Every element except the last value.
    
    Answer: 

    ```{r}

    ```

    1. Only even numbers (and no missing values).

    Answer: 

    ```{r}

    ```

5.  Why is `x[-which(x > 0)]` not the same as `x[x <= 0]`? 

    Answer: 

    ```{r}

    ```

6.  What happens when you subset with a positive integer that's bigger
    than the length of the vector? What happens when you subset with a 
    name that doesn't exist?

    Answer: 

    ```{r}

    ```

# Exercise 3

1.  Draw the following lists as nested sets:

    Answer: 

    ```{r}

    ```

    1.  `list(a, b, list(c, d), list(e, f))`
    Answer: 

    ```{r}

    ```

    1.  `list(list(list(list(list(list(a))))))`

    Answer: 

    ```{r}

    ```

2.  What happens if you subset a tibble as if you're subsetting a list?
    What are the key differences between a list and a tibble?

    Answer: 

    ```{r}

    ```

# Exercise 4

1.  What does `hms::hms(3600)` return? How does it print? What primitive
    type is the augmented vector built on top of? What attributes does it 
    use?
    
    Answer: 

    ```{r}

    ```

2.  Try and make a tibble that has columns with different lengths. What
    happens?

    Answer: 

    ```{r}

    ```

3.  Based on the definition above, is it ok to have a list as a
    column of a tibble?
    Answer: 

    ```{r}

    ```

