---
  title: "BIOS 611 HW5 Data import (Chapter 11)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

# Exercise 1

1.  What function would you use to read a file where fields were separated with  
    "|"?
    
    Answer: 

    ```{r}

    ```

2.  Apart from `file`, `skip`, and `comment`, what other arguments do
    `read_csv()` and `read_tsv()` have in common?
    
    Answer: 

    ```{r}

    ```

3.  What are the most important arguments to `read_fwf()`?
   
    Answer: 

    ```{r}

    ```

4.  Sometimes strings in a CSV file contain commas. To prevent them from
    causing problems they need to be surrounded by a quoting character, like
    `"` or `'`. By convention, `read_csv()` assumes that the quoting
    character will be `"`, and if you want to change it you'll need to
    use `read_delim()` instead. What arguments do you need to specify
    to read the following text into a data frame?
    
    ```{r, eval = FALSE}
    "x,y\n1,'a,b'"
    ```
    
    Answer: 

    ```{r}

    ```

5.  Identify what is wrong with each of the following inline CSV files. 
    What happens when you run the code?
    
    ```{r, eval = FALSE}
    read_csv("a,b\n1,2,3\n4,5,6")
    read_csv("a,b,c\n1,2\n1,2,3,4")
    read_csv("a,b\n\"1")
    read_csv("a,b\n1,2\na,b")
    read_csv("a;b\n1;3")
    ```

    Answer: 

    ```{r}

    ```

# Exercise 2

1.  What are the most important arguments to `locale()`? 

    Answer: 

    ```{r}

    ```

2.  What happens if you try and set `decimal_mark` and `grouping_mark` 
    to the same character? What happens to the default value of 
    `grouping_mark` when you set `decimal_mark` to ","? What happens
    to the default value of `decimal_mark` when you set the `grouping_mark`
    to "."?

    Answer: 

    ```{r}

    ```

3.  I didn't discuss the `date_format` and `time_format` options to
    `locale()`. What do they do? Construct an example that shows when 
    they might be useful.

    Answer: 

    ```{r}

    ```

4.  If you live outside the US, create a new locale object that encapsulates 
    the settings for the types of file you read most commonly.
    
    Answer: 

    ```{r}

    ```

5.  What's the difference between `read_csv()` and `read_csv2()`?
    
    Answer: 

    ```{r}

    ```

6.  What are the most common encodings used in Europe? What are the
    most common encodings used in Asia? Do some googling to find out.

    Answer: 

    ```{r}

    ```

7.  Generate the correct format string to parse each of the following 
    dates and times:
    
    ```{r}
    d1 <- "January 1, 2010"
    d2 <- "2015-Mar-07"
    d3 <- "06-Jun-2017"
    d4 <- c("August 19 (2015)", "July 1 (2015)")
    d5 <- "12/30/14" # Dec 30, 2014
    t1 <- "1705"
    t2 <- "11:15:10.12 PM"
    ```

    Answer: 

    ```{r}

    ```

