---
  title: "BIOS 611 HW7 Strings (Chapter 14)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

# Exercise 1

1.  In code that doesn't use stringr, you'll often see `paste()` and `paste0()`.
    What's the difference between the two functions? What stringr function are
    they equivalent to? How do the functions differ in their handling of 
    `NA`?
    
    Answer: 

    ```{r}

    ```

2.  In your own words, describe the difference between the `sep` and `collapse`
    arguments to `str_c()`.

    Answer: 

    ```{r}

    ```

3.  Use `str_length()` and `str_sub()` to extract the middle character from 
    a string. What will you do if the string has an even number of characters?

    Answer: 

    ```{r}

    ```

4.  What does `str_wrap()` do? When might you want to use it?

    Answer: 

    ```{r}

    ```

5.  What does `str_trim()` do? What's the opposite of `str_trim()`?

    Answer: 

    ```{r}

    ```

6.  Write a function that turns (e.g.) a vector `c("a", "b", "c")` into 
    the string `a, b, and c`. Think carefully about what it should do if
    given a vector of length 0, 1, or 2.

    Answer: 

    ```{r}

    ```

# Exercise 2

1.  Explain why each of these strings don't match a `\`: `"\"`, `"\\"`, `"\\\"`.

    Answer: 

    ```{r}

    ```

2.  How would you match the sequence `"'\`?

    Answer: 

    ```{r}

    ```

3.  What patterns will the regular expression `\..\..\..` match? 
    How would you represent it as a string?

    Answer: 

    ```{r}

    ```

# Exercise 3

1.  How would you match the literal string `"$^$"`?

    Answer: 

    ```{r}

    ```

2.  Given the corpus of common words in `stringr::words`, create regular
    expressions that find all words that:
    
    Answer: 

    ```{r}

    ```

    1. Start with "y".
    Answer: 

    ```{r}

    ```

    1. End with "x"
    Answer: 

    ```{r}

    ```

    1. Are exactly three letters long. (Don't cheat by using `str_length()`!)
    Answer: 

    ```{r}

    ```

    1. Have seven letters or more.

    Since this list is long, you might want to use the `match` argument to
    `str_view()` to show only the matching or non-matching words.

    Answer: 

    ```{r}

    ```

# Exercise 4

1.  Create regular expressions to find all words that:

    Answer: 

    ```{r}

    ```

    1. Start with a vowel.

    Answer: 

    ```{r}

    ```

    1. That only contain consonants. (Hint: thinking about matching 
       "not"-vowels.)

    Answer: 

    ```{r}

    ```

    1. End with `ed`, but not with `eed`.
    
    Answer: 

    ```{r}

    ```

    1. End with `ing` or `ise`.
    
    Answer: 

    ```{r}

    ```

2.  Empirically verify the rule "i before e except after c".

    Answer: 

    ```{r}

    ```

3.  Is "q" always followed by a "u"?

    Answer: 

    ```{r}

    ```

4.  Write a regular expression that matches a word if it's probably written
    in British English, not American English.

    Answer: 

    ```{r}

    ```

5.  Create a regular expression that will match telephone numbers as commonly
    written in your country.

    Answer: 

    ```{r}

    ```

# Exercise 5

1.  Describe the equivalents of `?`, `+`, `*` in `{m,n}` form.

    Answer: 

    ```{r}

    ```

2.  Describe in words what these regular expressions match:
    (read carefully to see if I'm using a regular expression or a string
    that defines a regular expression.)

    Answer: 

    ```{r}

    ```

    1. `^.*$`
    Answer: 

    ```{r}

    ```

    1. `"\\{.+\\}"`
    Answer: 

    ```{r}

    ```

    1. `\d{4}-\d{2}-\d{2}`
    Answer: 

    ```{r}

    ```

    1. `"\\\\{4}"`

    Answer: 

    ```{r}

    ```

3.  Create regular expressions to find all words that:

    Answer: 

    ```{r}

    ```

    1. Start with three consonants.
    Answer: 

    ```{r}

    ```

    1. Have three or more vowels in a row.
    Answer: 

    ```{r}

    ```

    1. Have two or more vowel-consonant pairs in a row.

    Answer: 

    ```{r}

    ```

4.  Solve the beginner regexp crosswords at
    <https://regexcrossword.com/challenges/beginner>.

    Answer: 

    ```{r}

    ```

# Exercise 6

1.  Describe, in words, what these expressions will match:

    Answer: 

    ```{r}

    ```

    1. `(.)\1\1`
    Answer: 

    ```{r}

    ```

    1. `"(.)(.)\\2\\1"`
    Answer: 

    ```{r}

    ```

    1. `(..)\1`
    Answer: 

    ```{r}

    ```

    1. `"(.).\\1.\\1"`
    Answer: 

    ```{r}

    ```

    1. `"(.)(.)(.).*\\3\\2\\1"`

    Answer: 

    ```{r}

    ```

2.  Construct regular expressions to match words that:

    Answer: 

    ```{r}

    ```

    1. Start and end with the same character.
    
    Answer: 

    ```{r}

    ```

    1. Contain a repeated pair of letters
       (e.g. "church" contains "ch" repeated twice.)
    
    Answer: 

    ```{r}

    ```

    1. Contain one letter repeated in at least three places
       (e.g. "eleven" contains three "e"s.)

    Answer: 

    ```{r}

    ```

# Exercise 7

1.  For each of the following challenges, try solving it by using both a single
    regular expression, and a combination of multiple `str_detect()` calls.
    
    Answer: 

    ```{r}

    ```

    1.  Find all words that start or end with `x`.
    
    Answer: 

    ```{r}

    ```

    1.  Find all words that start with a vowel and end with a consonant.
    
    Answer: 

    ```{r}

    ```

    1.  Are there any words that contain at least one of each different
        vowel?

    Answer: 

    ```{r}

    ```

2.  What word has the highest number of vowels? What word has the highest
    proportion of vowels? (Hint: what is the denominator?)

    Answer: 

    ```{r}

    ```

# Exercise 8

1.  In the previous example, you might have noticed that the regular
    expression matched "flickered", which is not a colour. Modify the 
    regex to fix the problem.

    Answer: 

    ```{r}

    ```

2.  From the Harvard sentences data, extract:

    Answer: 

    ```{r}

    ```

    1. The first word from each sentence.
    Answer: 

    ```{r}

    ```

    1. All words ending in `ing`.
    Answer: 

    ```{r}

    ```

    1. All plurals.

    Answer: 

    ```{r}

    ```

# Exercise 9

1. Find all words that come after a "number" like "one", "two", "three" etc.
   Pull out both the number and the word.

    Answer: 

    ```{r}

    ```

2. Find all contractions. Separate out the pieces before and after the 
   apostrophe.

    Answer: 

    ```{r}

    ```

# Exercise 10

1.   Replace all forward slashes in a string with backslashes.

    Answer: 

    ```{r}

    ```

2.   Implement a simple version of `str_to_lower()` using `replace_all()`.

    Answer: 

    ```{r}

    ```

3.   Switch the first and last letters in `words`. Which of those strings
     are still words?

    Answer: 

    ```{r}

    ```

# Exercise 11

1.  Split up a string like `"apples, pears, and bananas"` into individual
    components.
    
    Answer: 

    ```{r}

    ```

2.  Why is it better to split up by `boundary("word")` than `" "`?

    Answer: 

    ```{r}

    ```

3.  What does splitting with an empty string (`""`) do? Experiment, and
    then read the documentation.

    Answer: 

    ```{r}

    ```

# Exercise 12

1.  How would you find all strings containing `\` with `regex()` vs.
    with `fixed()`?

    Answer: 

    ```{r}

    ```

2.  What are the five most common words in `sentences`?

    Answer: 

    ```{r}

    ```

# Exercise 13

1.  Find the stringi functions that:

    Answer: 

    ```{r}

    ```

    1. Count the number of words.
    Answer: 

    ```{r}

    ```

    1. Find duplicated strings.
    Answer: 

    ```{r}

    ```

    1. Generate random text.

    Answer: 

    ```{r}

    ```

2.  How do you control the language that `stri_sort()` uses for 
    sorting?
    Answer: 

    ```{r}

    ```

