---
  title: "BIOS 611 HW6 Relational data (Chapter 13)"
  author: "(Your full name here)"
  date: "`r format(Sys.time(), '%m/%d/%Y')`"
  output: html_document
---

  This set of exercise is mostly taken from R for Data Science by Garrett Grolemund and Hadley Wickham.

# Exercise 1

1.  Imagine you wanted to draw (approximately) the route each plane flies from
    its origin to its destination. What variables would you need? What tables
    would you need to combine?

    Answer: 

    ```{r}

    ```

2.  I forgot to draw the relationship between `weather` and `airports`.
    What is the relationship and how should it appear in the diagram?

    Answer: 

    ```{r}

    ```

3.  `weather` only contains information for the origin (NYC) airports. If
    it contained weather records for all airports in the USA, what additional
    relation would it define with `flights`?

    Answer: 

    ```{r}

    ```

4.  We know that some days of the year are "special", and fewer people than
    usual fly on them. How might you represent that data as a data frame?
    What would be the primary keys of that table? How would it connect to the
    existing tables?

    Answer: 

    ```{r}

    ```

# Exercise 2

1.  Add a surrogate key to `flights`.

    Answer: 

    ```{r}

    ```

2.  Identify the keys in the following datasets

    Answer: 

    ```{r}

    ```

    1.  `Lahman::Batting`,
    Answer: 

    ```{r}

    ```

    1.  `babynames::babynames`
    Answer: 

    ```{r}

    ```

    1.  `nasaweather::atmos`
    Answer: 

    ```{r}

    ```

    1.  `fueleconomy::vehicles`
    Answer: 

    ```{r}

    ```

    1.  `ggplot2::diamonds`
    
    (You might need to install some packages and read some documentation.)

    Answer: 

    ```{r}

    ```

3.  Draw a diagram illustrating the connections between the `Batting`,
    `Master`, and `Salaries` tables in the Lahman package. Draw another diagram
    that shows the relationship between `Master`, `Managers`, `AwardsManagers`.

    How would you characterise the relationship between the `Batting`,
    `Pitching`, and `Fielding` tables?

    Answer: 

    ```{r}

    ```

# Exercise 3

1.  Compute the average delay by destination, then join on the `airports`
    data frame so you can show the spatial distribution of delays. Here's an
    easy way to draw a map of the United States:

    ```{r, eval = FALSE}
    airports %>%
      semi_join(flights, c("faa" = "dest")) %>%
      ggplot(aes(lon, lat)) +
        borders("state") +
        geom_point() +
        coord_quickmap()
    ```

    (Don't worry if you don't understand what `semi_join()` does --- you'll
    learn about it next.)

    You might want to use the `size` or `colour` of the points to display
    the average delay for each airport.

    Answer: 

    ```{r}

    ```

2.  Add the location of the origin _and_ destination (i.e. the `lat` and `lon`)
    to `flights`.

    Answer: 

    ```{r}

    ```

3.  Is there a relationship between the age of a plane and its delays?

    Answer: 

    ```{r}

    ```

4.  What weather conditions make it more likely to see a delay?

    Answer: 

    ```{r}

    ```

5.  What happened on June 13 2013? Display the spatial pattern of delays,
    and then use Google to cross-reference with the weather.

    ```{r, eval = FALSE, include = FALSE}
    worst <- filter(flights, !is.na(dep_time), month == 6, day == 13)
    worst %>%
      group_by(dest) %>%
      summarise(delay = mean(arr_delay), n = n()) %>%
      filter(n > 5) %>%
      inner_join(airports, by = c("dest" = "faa")) %>%
      ggplot(aes(lon, lat)) +
        borders("state") +
        geom_point(aes(size = n, colour = delay)) +
        coord_quickmap()
    ```

    Answer: 

    ```{r}

    ```

# Exercise 4

1.  What does it mean for a flight to have a missing `tailnum`? What do the
    tail numbers that don't have a matching record in `planes` have in common?
    (Hint: one variable explains ~90% of the problems.)

    Answer: 

    ```{r}

    ```

2.  Filter flights to only show flights with planes that have flown at least 100
    flights.

    Answer: 

    ```{r}

    ```

3.  Combine `fueleconomy::vehicles` and `fueleconomy::common` to find only the
    records for the most common models.

    Answer: 

    ```{r}

    ```

4.  Find the 48 hours (over the course of the whole year) that have the worst
    delays. Cross-reference it with the `weather` data. Can you see any
    patterns?

    Answer: 

    ```{r}

    ```

5.  What does `anti_join(flights, airports, by = c("dest" = "faa"))` tell you?
    What does `anti_join(airports, flights, by = c("faa" = "dest"))` tell you?

    Answer: 

    ```{r}

    ```

6.  You might expect that there's an implicit relationship between plane
    and airline, because each plane is flown by a single airline. Confirm
    or reject this hypothesis using the tools you've learned above.

    Answer: 

    ```{r}

    ```

